DATA 621 - Business Analytics and Data Mining

### 2020-11-07 HW4/HW4_Draft.Rmd
model #2 & copyediting

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #4'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg,
    Bryan Persaud, Jeff Shamp
date: "11/01/2020"
output:
  pdf_document:
    toc: TRUE
    toc_depth: 4
urlcolor: purple
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

```{r loadData, include=FALSE}
# Load necessary libraries
library(corrplot)
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(RANN)
library(pROC)
library(data.table)
# Set master seed
set.seed(71554)

@@

# Get the names of the variables and which ones are numeric
nmtrn <- names(DT)
nmtrnNUM <- names(DT[, .SD, .SDcols = sapply(DT, is.numeric)])
nmtrnDUB <- names(DT[, .SD, .SDcols = sapply(DT, is.double)])
nmtrnFAC <- setdiff(nmtrn, nmtrnNUM)
# Drop INDEX and target variablesfrom name list
nmtrnNUM <- nmtrnNUM[-(1:3)]
```

@@

|VARIABLE NAME|DEFINITION|THEORETICAL EFFECT|
|-|-|-|
|INDEX|Identification Variable (do not use)|None|
|TARGET_FLAG|Was Car in a crash? 1=YES 0=NO|None|
|TARGET_AMT|If car was in a crash, what was the cost|None|
|AGE|Age of Driver|Very young people tend to be risky. Maybe very old people also.|
|BLUEBOOK|Value of Vehicle|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_AGE|Vehicle Age|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_TYPE|Type of Car|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_USE|Vehicle Use|Commercial vehicles are driven more, so might increase probability of collision|
|CLM_FREQ|# Claims (Past 5 Years)|The more claims you filed in the past, the more you are likely to file in the future|
|EDUCATION|Max Education Level|Unknown effect, but in theory more educated people tend to drive more safely|
|HOMEKIDS|# Children at Home|Unknown effect|
|HOME_VAL|Home Value|In theory, home owners tend to drive more responsibly|
|INCOME|Income|In theory, rich people tend to get into fewer crashes|
|JOB|Job Category|In theory, white collar jobs tend to be safer|
|KIDSDRIV|# Driving Children|When teenagers drive your car, you are more likely to get into crashes|
|MSTATUS|Marital Status|In theory, married people drive more safely|
|MVR_PTS|Motor Vehicle Record Points|If you get lots of traffic tickets, you tend to get into more crashes|
|OLDCLAIM|Total Claims (Past 5 Years)|If your total payout over the past five years was high, this suggests future payouts will be high|
|PARENT1|Single Parent|Unknown effect|
|RED_CAR|A Red Car|Urban legend says that red cars (especially red sports cars) are more risky. Is that true?|
|REVOKED|License Revoked (Past 7 Years)|If your license was revoked in the past 7 years, you probably are a more risky driver.|
|SEX|Gender|Urban legend says that women have less crashes then men. Is that true?|
|TIF|Time in Force|People who have been customers for a long time are usually more safe.|
|TRAVTIME|Distance to Work|Long drives to work usually suggest greater risk|
|URBANICITY|Home/Work Area|Unknown|
|YOJ|Years on Job|People who stay at a job for a long time are usually more safe|

@@

A variable such as `OLDCLAIM` is expected to have a mass point at 0. Every
observation which had fewer than 2 claims clearly did not have a prior claim!

### Factor Predictors
While tabular depiction of factor variables is usually of little value, visual
representation of their distributions is of use.

@@

 * `HOMEKIDS` with `KIDSDRIV`
   * This is self-explanatory
 * `HOME_VAL` with `INCOME`
   * Both are very strongly tied to wealth and net worth
 * `BLUEBOOK` with`INCOME`
   * People with more disposable income can afford more expensive vehicles
 * `CLM_FREQ` with `OLDCLAIM`
   * More claims implies a greater total aggregate payment
 * `CAR_AGE` with `INCOME`
   * This is interesting. It could be that people with higher disposable incomes
   buy more expensive cars and keep them for longer, but that's a guess.
 * `MVR_PTS` is *lightly* correlated with `CLM_FREQ` and `OLDCLAIM`
   * Probably when one is in a lot of accidents, the chances of them being at
   some level of fault rises
 * `HOMEKIDS` **negatively** correlated with `AGE`
   * As people age, their children age as well and eventually move out, we hope!

@@

However, there will need to be two sets of training and testing, as the severity
model must perforce be trained on data for which a claim occurred. To maintain
integrity, the split of all the data for frequency will be honored for severity.
The 70/30 split will be honored as all claims with a `TARGET_FLAG` of 1 will
have non-zero `TARGET_AMT`, However, there will be no guarantee that the
*distribution* of the loss conditional on event in the validation set will be
similar to the training set as a whole.

@@

## Models Set 1
### Missing Data
The issues with factor data were handled universally for all models through
resetting the levels. What remains is handling the missing numeric values. For
`CAR_AGE` simple k-means imputation will be used. The remaining three problem
variables, `YOJ`, `INCOME`, and `HOME_VAL` have both `NA` and 0 issues.

@@

We will take a different approach with `HOME_VAL`. As seen above when the 0
values are removed, `HOME_VAL` has a nice lognormal shape. It is also reasonable
to consider that people responding with 0 for `HOME_VAL` are non-owners as
opposed to it being missing, although we would want to investigate this further
were we allowed. Therefore, we are going to add a "Own" variable which will be
`Yes` for all positive `HOME_VAL` and `No` otherwise, and allow an interaction
between this value and the actual value. This would be much more effective in a
decision tree framework, but that is not available.

@@

@@

 * Three-way interaction between `OWN`, `HOME_VAL` and `INCOME`
   * Represents wealth
 * Three-way interaction between `CLM_FREQ`, `OLDCLAIM`, and `MVR_PTS`
   * Represents prior history
 * `CAR_USE` with `URBANICITY`
   * Represents increased risk of location

@@

#### Training
At this point the code will be set up to preprocess the data and train the
model. The two pre-processing steps which will be done will be to check for
near-zero variance between the predictors and then use kNN imputations for
missing values. Even though the `caret` package allows the preprocessing to
occur in the call to `train`, it will be seperated here for clarity. The actual
code may be found in the CODE APPENDIX.

@@

Most of the coefficients are of the expected direction. For example, having
one's license revoked, living in an urban area, or increased travel times are
all *positive* risk factors while higher levels of wealth or being married are
*negative* risk factors.

@@

Every level of the interactions between `CLM_FREQ`, `OLDCLAIM`, and `MVR_PTS`
are significant.  What this may be telling us is that a linear regression is
***not*** the proper model for this analysis, and the algorithm is struggling to
add non-linearity via the interactions.

@@

#### Training
The observations in the training set which have claim amounts greater than 0
will be extracted and used to fit the linear regression. Similar to frequency,
the model will be selected via a forward and backward stepwise AIC algorithm
starting with the all the predictors. Experimentation with interactions only had
worse effects, so no interaction will be considered.

@@

#### Coefficient Disucssion
It is not surprising that this model has many fewer predictors. Information
which helps in identifying the *existence* of a claim often does not help in
estimating the *magnitude* of the claim.

@@

Unlike the frequency model, many of the resulting predictors are not significant
at even the 10% level. What this may be telling us is that a linear regression is
***not*** the proper model for this analysis, and the algorithm is struggling to
add non-linearity via the interactions. In practice, at the very least a GLM
with a gamma link would be tried or, more sophisticated predictive models such
as tree-based ones would be investigated. Most likely, MLE would be used to
estimate severity and a hierarchial contingent stocahstic cash flow model would
be built such that given a claim, a loss would be generated from a much more
amenable distribution, such as a Pareto or a Burr.

#### Variable Importance
In terms of variable importance, it can be estimated from the the last trace of
the stepping procedure shown below. The further down the list a variable
preceded by a `-` is, the more drastic of an effect its removal would have on
the model AIC.

@@

# SELECT MODELS
## Model Selection Criteria
For that *classification* algorithm, we will look at accuracy, AUC, and F1, and
select the model which performs best two out of three in those metrics. For the
*regression* algorithm we will look at RMSE and MAE (since the values must
be positive) and select the model which performs best on both, Ties will be
broken by adjusted \(R^2\).

@@

## Model 2
### Frequency Model
### Severity Model

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r zeroVal}
```
```{r statsN}
```
```{r graphsN}
```
```{r graphsF}
```
```{r corrgram}
```
```{r dataClean}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r model1DummyFreq}
```
```{r model1RunFreq}
```
```{r model1DummySev}
```
```{r model1RunSev}
```
```{r setUpCompTables}
```
```{r validateM1F}
```
```{r validateM1S}
```
```{r freqComp}
```
```{r sevComp}
```

>>>>

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #4'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg,
    Bryan Persaud, Jeff Shamp
date: "11/08/2020"
output:
  pdf_document:
    toc: TRUE
    toc_depth: 4
urlcolor: purple
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, error=FALSE, warning=FALSE, message=FALSE)
```

```{r loadData, include=FALSE}
# Load necessary libraries
library(corrplot)
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(RANN)
library(pROC)
library(data.table)
library(mice)

# Set master seed
set.seed(71554)

@@

# Get the names of the variables and which ones are numeric
nmtrn <- names(DT)
nmtrnNUM <- names(DT[, .SD, .SDcols = sapply(DT, is.numeric)])
nmtrnDUB <- names(DT[, .SD, .SDcols = sapply(DT, is.double)])
nmtrnFAC <- setdiff(nmtrn, nmtrnNUM)
# Drop INDEX and target variables from name list
nmtrnNUM <- nmtrnNUM[-(1:3)]
```

@@

|VARIABLE NAME|DEFINITION|THEORETICAL EFFECT|
|-|-|--|
|INDEX|Identification Variable (do not use)|None|
|TARGET_FLAG|Was Car in a crash? 1=YES 0=NO|None|
|TARGET_AMT|If car was in a crash, what was the cost|None|
|AGE|Age of Driver|Very young people tend to be risky. Maybe very old people also.|
|BLUEBOOK|Value of Vehicle|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_AGE|Vehicle Age|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_TYPE|Type of Car|Unknown effect on probability of collision, but probably effect the payout if there is a crash|
|CAR_USE|Vehicle Use|Commercial vehicles are driven more, so might increase probability of collision|
|CLM_FREQ|# Claims (Past 5 Years)|The more claims you filed in the past, the more you are likely to file in the future|
|EDUCATION|Max Education Level|Unknown effect, but in theory more educated people tend to drive more safely|
|HOMEKIDS|# Children at Home|Unknown effect|
|HOME_VAL|Home Value|In theory, home owners tend to drive more responsibly|
|INCOME|Income|In theory, rich people tend to get into fewer crashes|
|JOB|Job Category|In theory, white collar jobs tend to be safer|
|KIDSDRIV|# Driving Children|When teenagers drive your car, you are more likely to get into crashes|
|MSTATUS|Marital Status|In theory, married people drive more safely|
|MVR_PTS|Motor Vehicle Record Points|If you get lots of traffic tickets, you tend to get into more crashes|
|OLDCLAIM|Total Claims (Past 5 Years)|If your total payout over the past five years was high, this suggests future payouts will be high|
|PARENT1|Single Parent|Unknown effect|
|RED_CAR|A Red Car|Urban legend says that red cars (especially red sports cars) are more risky. Is that true?|
|REVOKED|License Revoked (Past 7 Years)|If your license was revoked in the past 7 years, you probably are a more risky driver.|
|SEX|Gender|Urban legend says that women have less crashes then men. Is that true?|
|TIF|Time in Force|People who have been customers for a long time are usually more safe.|
|TRAVTIME|Distance to Work|Long drives to work usually suggest greater risk|
|URBANICITY|Home/Work Area|Unknown|
|YOJ|Years on Job|People who stay at a job for a long time are usually more safe|

@@

A variable such as `OLDCLAIM` is expected to have a mass point at 0. Every
observation that had fewer than 2 claims clearly did not have a prior claim!

### Factor Predictors
While a tabular depiction of factor variables is usually of little value, visual
representation of their distributions is of use.

@@

 * `HOMEKIDS` with `KIDSDRIV`
   * This is self-explanatory.
 * `HOME_VAL` with `INCOME`
   * Both are very strongly tied to wealth and net worth.
 * `BLUEBOOK` with`INCOME`
   * People with more disposable income can afford more expensive vehicles.
 * `CLM_FREQ` with `OLDCLAIM`
   * More claims implies a greater total aggregate payment.
 * `CAR_AGE` with `INCOME`
   * This is interesting. It could be that people with higher disposable incomes
   buy more expensive cars and keep them for longer, but that's a guess.
 * `MVR_PTS` is *lightly* correlated with `CLM_FREQ` and `OLDCLAIM`
   * Probably when one is in a lot of accidents, the chances of them being at
   some level of fault rises.
 * `HOMEKIDS` **negatively** correlated with `AGE`
   * As people age, their children age as well and eventually move out, we hope!

@@

However, there will need to be two sets of training and testing, as the severity
model must perforce be trained on data for which a claim occurred. To maintain
integrity, the split of all the data for frequency will be honored for severity.
The 70/30 split will be honored as all claims with a `TARGET_FLAG` of 1 will
have non-zero `TARGET_AMT`. However, there will be no guarantee that the
*distribution* of the loss conditional on the event in the validation set will be
similar to the training set as a whole.

@@

## Model Set #1
### Missing Data
The issues with factor data were handled universally for all models through
resetting the levels. What remains is handling the missing numeric values. For
`CAR_AGE` simple k-means imputation will be used. The remaining three problem
variables, `YOJ`, `INCOME`, and `HOME_VAL` have both `NA` and 0 issues.

@@

We will take a different approach with `HOME_VAL`. As seen above when the 0
values are removed, `HOME_VAL` has a nice lognormal shape. It is also reasonable
to consider that people responding with 0 for `HOME_VAL` are non-owners as
opposed to it being missing, although we would want to investigate this further
were we allowed. Therefore, we are going to add an "Own" variable which will be
`Yes` for all positive `HOME_VAL` and `No` otherwise, and allow an interaction
between this value and the actual value. This would be much more effective in a
decision tree framework, but that is not available.

@@

## Model Set #2  
### Missing Data

Like Model Set #1, the data preparation efforts for Model Set #2 also includes the 
imputation of missing values for the predictor variables. However, because it combines 
the standard linear regression and the nearest-neighbor imputation approach, Model Set #2 
elected to fill in missing values of a continuous variable by using the predictive mean 
matching imputation method. Moreover, there will be the derivation of three new binary 
factor variables.

* `AGE`  
  + Since the data set is comprised of auto insurance policyholder information, the 
  missing `AGE` values required imputation. However, given the relatively small number 
  of missing values, imputation by predictive mean matching is conducted.

* `HOME_VAL`  
  + A `HOME_VAL` response of '0' makes it understandable to assume that those missing 
  entries could indicate that the policyholder is a renter rather than a homeowner. 
  Therefore, missing values were replaced with zeroes. The new `OWN` variables created 
  in Model Set #1 is kept in Model Set #2.

* `CAR_AGE`, `INCOME` & `YOJ`  
  + Because there is a larger number of missing values (NA’s) were identified, 
  imputation by predictive mean matching is conducted.

  + Moreover, there is a single negative value ('-3') for `CAR_AGE` which seemed 
  implausible and was assumed to be a typographical error. Thus, the absolute value 
  of `CAR_AGE` is taken.

### New Variables

For Model Set #2, new factor variables ($VARIABLE`.f`) were create as a way to better 
capture policyholder's profile in the binary logistic regression modeling process.

* `CAR_AGE.f`  
  + Because `CAR_AGE` is dominated by values of 1 (i.e. car being one year old or less), 
  the `CAR_AGE.f` variable is derived as a factor variable to be used during the binary 
  logistic regression modeling process. Therefore, it is interpreted as:

    `CAR_AGE.f` = 0: The vehicle is 1 year old or less.  
    `CAR_AGE.f` = 1: The vehicle is more than a 1-year-old.

* `HOMEKIDS.f` & `KIDSDRIV.f` 
   + Both the `HOMEKIDS` and `KIDSDRIV` variables indicated that large percentages of the 
   values of each were 0. Therefore, both variables were converted to binary variables. 
   The following is their binary interpretations:

      `HOMEKIDS.f` = 0: The policyholder has no child living at home.  
      `HOMEKIDS.f` = 1: The policyholder has 1 or more children living at home.  
      `KIDSDRIV.f` = 0: No teenage drivers use the policyholder’s insured vehicle.  
      `KIDSDRIV.f` = 1: One or more teenage drivers use the policyholder’s insured vehicle.

```{r m2clean}
# Clean Training set
m2.train.X <- trnX
m2.train.X$HOME_VAL[is.na(m2.train.X$HOME_VAL)] <- 0
m2.train.X$OWN[is.na(m2.train.X$OWN)] <- "No"
m2.train.X$CAR_AGE = abs(m2.train.X$CAR_AGE) 
m2.train.r <- factor(m2.train.X$TARGET_FLAG, levels = c(0, 1), 
                     labels = c("NoClaim", "Claim"))
m2.train.X.impute <- mice(m2.train.X, method = 'pmm', print = FALSE)
m2.train.X <- complete(m2.train.X.impute)
m2.train.X$CAR_AGE.f <- factor(ifelse(m2.train.X$CAR_AGE > 1, 1, 0),
                              levels = c(0, 1), 
                              labels = c('1 Year or less', 'More than a Year'))
m2.train.X$HOMEKIDS.f <- factor(ifelse(m2.train.X$HOMEKIDS >= 1, 1, 0),
                              levels = c(0, 1), 
                              labels = c('None', 'At least 1'))
m2.train.X$KIDSDRIV.f <- factor(ifelse(m2.train.X$KIDSDRIV >= 1, 1, 0),
                              levels = c(0, 1), 
                              labels = c('None', 'At least 1'))
m2.train.p <- m2.train.X[, -c(1:3)]

# Clean Test Set
m2.test.X <- tstX
m2.test.X$HOME_VAL[is.na(m2.test.X$HOME_VAL)] <- 0
m2.test.X$OWN[is.na(m2.test.X$OWN)] <- "No"
m2.test.X$CAR_AGE = abs(m2.test.X$CAR_AGE) 
m2.test.r <- factor(m2.test.X$TARGET_FLAG, levels = c(0, 1), 
                     labels = c("NoClaim", "Claim"))
m2.test.X.impute <- mice(m2.test.X, method = 'pmm', print = FALSE)
m2.test.X <- complete(m2.test.X.impute)
m2.test.X$CAR_AGE.f <- factor(ifelse(m2.test.X$CAR_AGE > 1, 1, 0),
                              levels = c(0, 1), 
                              labels = c('1 Year or less', 'More than a Year'))
m2.test.X$HOMEKIDS.f <- factor(ifelse(m2.test.X$HOMEKIDS >= 1, 1, 0),
                              levels = c(0, 1), 
                              labels = c('None', 'At least 1'))
m2.test.X$KIDSDRIV.f <- factor(ifelse(m2.test.X$KIDSDRIV >= 1, 1, 0),
                              levels = c(0, 1), 
                              labels = c('None', 'At least 1'))
m2.test.p <- m2.test.X[, -c(1:3)]
```

@@

 * Three-way interaction between `OWN`, `HOME_VAL` and `INCOME`
   * Represents wealth
 * Three-way interaction between `CLM_FREQ`, `OLDCLAIM`, and `MVR_PTS`
   * Represents a prior history
 * `CAR_USE` with `URBANICITY`
   * Represents increased risk of location

@@

#### Training  
At this point, the code will be set up to preprocess the data and train the
model. The two pre-processing steps which will be done will be to check for
near-zero variance between the predictors and then use kNN imputations for
missing values. Even though the `caret` package allows the preprocessing to
occur in the call to `train`, it will be separated here for clarity. The actual
code may be found in the CODE APPENDIX.

@@

Most of the coefficients are in the expected direction. For example, having
one's license revoked, living in an urban area, or increased travel times are
all *positive* risk factors while higher levels of wealth or being married are
*negative* risk factors.

@@

Every level of the interactions between `CLM_FREQ`, `OLDCLAIM`, and `MVR_PTS`
are significant.  What this may be telling us is that linear regression is
***not*** the proper model for this analysis and the algorithm is struggling to
add non-linearity via the interactions.

@@

#### Training  
The observations in the training set which have claim amounts greater than 0
will be extracted and used to fit the linear regression. Similar to frequency,
the model will be selected via a forward and backward stepwise AIC algorithm
starting with all the predictors. Experimentation with interactions only had
worse effects, so no interaction will be considered.

@@

#### Coefficient Disucssion  
It is not surprising that this model has fewer predictors. Information which 
helps in identifying the *existence* of a claim often does not help in
estimating the *magnitude* of the claim.

@@

Unlike the frequency model, many of the resulting predictors are not significant
at even the 10% level. What this may be telling us is that linear regression is
***not*** the proper model for this analysis and the algorithm is struggling to
add non-linearity via the interactions. In practice, at the very least a GLM
with a gamma link would be tried or, more sophisticated predictive models such
as tree-based ones would be investigated. Most likely, MLE would be used to
estimate the severity and a hierarchial contingent stochastic cash flow model would
be built such that given a claim, a loss would be generated from a much more
amenable distribution, such as a Pareto or a Burr.

#### Variable Importance
In terms of variable importance, it can be estimated from the last trace of
the stepping procedure shown below. The further down the list a variable
preceded by a `-` is, the more drastic of an effect its removal would have on
the model AIC.

@@

## Model Set #2
### Frequency Model

The frequency model is built to determine whether a vehicle is likely to crash. In Model 
Set #2, to work with complete separation in the logistic regression model, a Bayesian analysis 
is fitted. The Bayesian statistical model returns samples of the parameters of interest (the
"posterior" distribution) based on some "prior" distribution which is then updated by the 
data. Here, Cauchy distribution is accepted as a prior for parameters of the generalized 
linear model.

```{r model2RunFreq}
# Train Model Set #2
set.seed(525)
m2FreqFit <- train(x = m2.train.p, y = m2.train.r, 
                   trControl = trainControl(method = 'repeatedcv',
                                            classProbs = TRUE, 
                                            number = 10),
                   method = 'bayesglm', family = 'binomial')
# Results
kable(summary(m2FreqFit$finalModel)$coefficients, digits = 3L,
      caption = "Model 2 Frequency Regression Output")
```

#### Coefficient Discussion

Contributing coefficients are those which lie within the 95% level of significance. A 
positive coefficient indicates that as the value of the predictor increases, the response 
variable also tends to increase. A negative coefficient suggests that as the predictor 
increases, the response variable tends to decrease.

Immediately, the model follows the suggested theories behind specific variables. For example,
policyholders who are married, have a higher income and an old claim is less likely to be 
involved in an accident. Moreover, more educated, at least with a Bachelor’s degree, 
policyholders drive more safely. The higher the bluebook value of the policyholder’s vehicle, 
it decreases the probability of a claim. This makes sense naturally since more intelligent 
individuals would seek to protect relatively valuable assets they are responsible for. Last, 
the longer a policyholder has been a customer of the company, the less likely they are to be 
involved in an accident. Since insurance companies would typically impose larger rates or 
cancel the policies of careless drivers.

On the contrary, and unsurprising, policyholders who have previously had their driver’s licenses 
revoked increases the probability of a claim. This parallels the result that the more motor 
vehicle record points a policyholder has gained, they are assumed to be unsafe drivers and are 
more likely to be involved in an accident. If a policyholder lives in an urban area, they are
prone to an accident since traffic and pedestrian congestion are more common. Another expected 
result, is that the longer a policyholder’s commute to work is, there is an increased likelihood 
of a driver being involved in an accident. The last connection that can be inferred is that 
drivers of a larger type of vehicles are more prone to accidents than are drivers of other 
types of vehicles, with minivans being the least prone. The results seem to suggest that owners
of sports cars and SUVs are riskier types of drivers. Interestingly, commercial usage of 
vehicle present critical reason for more frequent accidents to occur because of driver error 
or non-performance, and failure to maintain vehicle causing issues or malfunction.

Similar to Model Set #1, the multivariate linear regression model used the data set’s 
`TARGET_AMT` attribute as the response variable and the data was split to include only those
records that have a claim. The elastic net is a regularized regression method that linearly 
combines the L1 and L2 regularization penalties. Predictors, specifically qualitative variables,
were automatically transformed into dummy variables, which is important because `glmnet()` can 
only take numerical, quantitative inputs. Cross-validation is done on different combinations 
of $\lambda_1$ and $\lambda_2$ to find the best values. The hybrid elastic net regression is 
especially good at dealing with situations when there are correlations between parameters.

```{r model2RunSev}
# Train Model Set #2
temp <- split(m2.train.X, m2.train.X$TARGET_AMT > 0)[[2]] 
m2.train.r <- temp$TARGET_AMT
m2.train.p <- model.matrix(temp$TARGET_AMT~., temp[, -c(1:3)])[,-1]
set.seed(525)
m2SevFit <- train(x = m2.train.p, y = m2.train.r, 
                   trControl = trainControl(method = 'repeatedcv',
                                            number = 10),
                   method = 'glmnet',
                   tuneLength = 10,
                   preProcess = c("center", "scale"))
# Results
coeffs = coef(m2SevFit$finalModel, m2SevFit$bestTune$lambda)
kable(data.frame(cbind(variables = coeffs@Dimnames[[1]][coeffs@i+1], 
                       coef = round(coeffs@x,3))), 
      caption = "Model 2 Severity Regression Output")
```

#### Coefficient Disucssion

Once again, contributing coefficients are those which lie within the 95% level of significance. 
In this case, the linear model reduced the number of predictors that can predict the cost given 
an accident. The model fits extremely poor and does a mediocre job at explaining the variability 
within the training data. If interpretations are still to be made, first, the intercept itself 
suggests that with no information on the policyholder, given a vehicle accident, the likely claim 
value to the individual is $5,728. The other predictors suggest that the higher the bluebook value 
of the policyholder’s vehicle, the larger the insurance payout will be in the event of an accident. 
If they use the vehicle for commercial, they will also have a larger claim amount. While being a 
female resulted as a significant variable, its coefficient is near zero and will be ignored.

# SELECT MODELS
## Model Selection Criteria
For that *classification* algorithm, we will look at accuracy, AUC, and F1, and
select the model which performs best two out of three in those metrics. For the
*regression* algorithm, we will look at RMSE and MAE (since the values must
be positive) and select the model which performs best on both, Ties will be
broken by adjusted \(R^2\).

@@

## Model 2
### Frequency Model

```{r validateM2F}
# Model 2 Frequency
# Prediction
m2Fpred <- predict(m2FreqFit, newdata = m2.test.X)
m2FpredProb <- predict(m2FreqFit, newdata = m2.test.X, type = 'prob')

# Accuracy Statistics
m2FCM <- confusionMatrix(m2Fpred, m2.test.r, mode = 'everything')
freqCompTable[2, 2] <- m2FACC <- sum(diag(m2FCM$table)) / sum(m2FCM$table)
freqCompTable[2, 3] <- m2FF1 <- m2FCM$byClass[7]
freqCompTable[2, 4] <- m2FAUC <- auc(response = m2.test.r,
                                     predictor = m2FpredProb[, 1])
m2FCM$table
```

Frequency Model 2 returns an accuracy of `r round(m2FACC, 4)`, an F1 score of
`r round(m2FF1, 4)`, and an AUC of `r round(m2FAUC, 4)`.

```{r validateM2S}
# Model 2 Severity
temp <- split(m2.test.X, m2.test.X$TARGET_AMT > 0)[[2]] 
m2.test.r <- temp$TARGET_AMT
m2.test.p <- model.matrix(temp$TARGET_AMT~., temp[, -c(1:3)])[,-1]

# Prediction
m2Spred <- predict(m2SevFit, newdata = m2.test.p)

# Accuracy Statistics
m2Ssum <- postResample(m2Spred, tstSev)
sevCompTable[2, 2] <- m2SRMSE <- RMSE(m2Spred, m2.test.r)
sevCompTable[2, 3] <- m2SMAE <- MAE(m2Spred, m2.test.r)
sevCompTable[2, 4] <- m2SAR2 <- R2(m2Spred, m2.test.r)
```

Severity Model 2 returns an RMSE of `r round(m2SRMSE, 1)`, an MAE of
`r round(m2SMAE, 1)`, and an adjusted \(R^2\) of `r round(m2SAR2, 4)`.

@@

# CODE APPENDIX
```{r setup2, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, eval=FALSE)
```
```{r loadData}
```
```{r missingVal}
```
```{r zeroVal}
```
```{r statsN}
```
```{r graphsN}
```
```{r graphsF}
```
```{r corrgram}
```
```{r dataClean}
```
```{r trainTestSplit}
```
```{r model1addVars}
```
```{r m2clean}
```
```{r model1DummyFreq}
```
```{r model1RunFreq}
```
```{r model1DummySev}
```
```{r model1RunSev}
```
```{r model2RunFreq}
```
```{r model2RunSev}
```
```{r setUpCompTables}
```
```{r validateM1F}
```
```{r validateM1S}
```
```{r validateM2F}
```
```{r validateM2S}
```
```{r freqComp}
```
```{r sevComp}
```
